Lyman-$\alpha$ photons through rotating outflows

### 2018-08-09 paper/paper.tex
obs params

The Monte Carlo code we use (CLARA) \citep{CLARA} follows the propagation of
individual photons through a neutral Hydrogen medium characterized by
its temperature, velocity field and global optical depth.
The code assumes a homogeneous density throughout the simulated
volume.
In the current implementation we neglect the influence of dust.
Our basic model is an spherical distribution of neutral hydrogen,
an approximation commonly used in the literature, as it explains a
wide variety of observational features
\citep{Ahn03,Verhamme06,Dijkstra06}.

The velocity field we use captures both outflows and rotation.
Outflows are described by a Hubble-like radial velocity profile with
the velocity magnitude increasing linearly with the radial
coordinate; the outflows model is fully characterized by $v_{\rm out}$, the
radial velocity at the sphere's surface.
Rotation follows a solid body rotation profile, which is fully
characterized by $v_{\rm rot}$, the linear velocity at the sphere's surface.

@@

For each model setup we follow $10^5$ individual photons generated at
the center of the sphere at the \lya line's center as they propagate
through the volume and finally escape.
We store the final frequency and propagation direction for each photon
at its last scattering.

As input parameters we use $\tauh=\{10^5, 10^6, 10^7\}$,
$\vout=\{5,25,50\}\;\kms$ and $\vrot=\{0,50,100\}\;\kms$, for a total of
$27$ models with all the possible parameter combinations.
The range of values have some overlap with the expectations from a
galaxy with a total neutral hydrogen mass of $10^8$-$10^9$
$M_{\odot}$. We also define the viewing angle, $\theta$, as the angle
between the rotation axis and the line of sight of a potential observer.

@@

\subsection{\lya Kinematic Maps}

Current observational facilities have the capability of spatially
resolving the extent of a LAE.
For instance \cite{Prescott14} presented observational results of a
Doppler shift when taking spectra at two opposite sides of a large
($\approx 80$kpc) LAE.
In more recent work \cite{2018MNRAS.473.3907A} mapped \lya emission
around a quasar.

>>>>

We use (CLARA) \citep{CLARA}, a Monte Carlo code that follows the
propagation of individual photons through a neutral Hydrogen medium
characterized by  its temperature, velocity field and global optical depth.
The code assumes an homogeneous density throughout the simulated volume.
In the current implementation we neglect the influence of dust.
Our basic model is an spherical distribution of neutral hydrogen,
an approximation commonly used in the literature, as it explains a
wide variety of observational features
\citep{Ahn03,Verhamme06,Dijkstra06}.

The velocity field we use captures both outflows and rotation.
Outflows are described by a Hubble-like radial velocity profile with
the velocity magnitude increasing linearly with the radial
coordinate; this model is fully characterized by $v_{\rm out}$, the
radial velocity at the sphere's surface.
Rotation follows a solid body rotation profile, which is fully
characterized by $v_{\rm rot}$, the linear velocity at the sphere's surface.

@@

For each model setup we follow $10^5$ individual photons generated from
the center of the sphere at the \lya line's center as they propagate
through the volume and finally escape.
We store the frequency and propagation direction for each photon
at its last scattering.

As input parameters we use $\tauh=\{10^5, 10^6, 10^7\}$,
$\vout=\{5,25,50\}\;\kms$ and $\vrot=\{0,50,100\}\;\kms$, for a total of
$27$ models with all the possible parameter combinations.
The values for the outflow velocity are lower than other values used in the
literature to allow for an interplay between the two kinematic features.
Nevertheless, this range of parameters reproduces the main standard
deviation and skewness  of high redshift LAES in recent observations
(\label{subsec:kinematic}).

We also define the viewing angle, $\theta$, as the angle
between the rotation axis and the line of sight of a potential observer.

@@

\subsection{\lya Kinematic Maps}
\label{subsec:kinematic}
Current observational facilities have the capability of spatially
resolving the extent of a LAE.
For instance \cite{Prescott14} presented observational results of a
Doppler shift when taking spectra at two opposite sides of a large
($\approx 80$kpc) LAE.
In more recent work \cite{2018MNRAS.473.3907A} mapped \lya emission
around a quasar.
